---
title: "Project"
author: "SANKUNG"
date: "`r Sys.Date()`"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r}
# Load the libraries
library(twang)
library(WeightIt)
library(dplyr)
library(ggplot2)
```





$ In a randomized controlled trial (RCT), the potential outcomes can be related to the treatment assignment variable \(D\) as follows:
\[
Y_i = Y_i^0 + (Y_i^1 - Y_i^0)D_i
\]
where \(D_i\) is a binary variable indicating treatment assignment for marketing campaign (1 for treatment, 0 for control), and \(Y_i\) is the observed outcome for individual \(i\). The potential outcomes \(Y_i^0\) and \(Y_i^1\) represent what the outcome would be under control and treatment, respectively. The Average Treatment Effect (ATE) is then given by:
\[
ATE = E[Y_i^1 - Y_i^0] = E[Y_i|D=1] - E[Y_i|D=0]
\]$

```{r}
df <- read.csv("/Users/sankungfatty/Desktop/R Files/bank.csv")
tail(df)
```

 

```{r}
# Data preparation
df$deposit <- factor(df$deposit, levels = c("no", "yes"))
df$education <- factor(df$education, levels = c("primary", "secondary", "tertiary", "unknown"))

# Plotting
par(mfrow=c(1,2), mar=c(4,4,2,2))  # Setting up the layout

# Pie chart
pie_data <- table(df$deposit)
colors <- c("#FA5858", "#64FE2E")
labels <- c("Did not Open Term Subscriptions", "Opened Term Subscriptions")

pie(pie_data, labels = labels, col = colors, main = "Information on Term Subscriptions", cex.main = 1.5,
    cex = 1.2, explode = c(0, 0.25), 
    percent = "%1.2f%%", shadow = TRUE, angle = 25)

# Bar chart
bar_data <- df %>% 
  group_by(education, deposit) %>% 
  summarize(count = n()) %>% 
  mutate(percentage = count / sum(count) * 100)

bar_plot <- ggplot(bar_data, aes(x = education, y = percentage, fill = deposit)) +
  geom_bar(stat = "identity", position = "dodge") +
  labs(title = "Information on Term Subscriptions",
       y = "(%)",
       x = "Education Level") +
  theme_minimal()

print(bar_plot)

```
```{r}
# Set up the base plot
fig <- ggplot() + theme_minimal() + theme(plot.title = element_text(hjust = 0.5))

# Subplot 1
fig <- fig + geom_boxplot(data = df, aes(x = default, y = balance, fill = deposit), width = 0.7) +
  labs(title = "Amount of Balance by Term Subscriptions") +
  scale_fill_manual(values = c("#FA5858", "#64FE2E"), name = "Deposit")

# Subplot 2
fig <- fig + geom_boxplot(data = df, aes(x = job, y = balance, fill = deposit), width = 0.7) +
  labs(title = "Type of Work by Term Subscriptions") +
  scale_fill_manual(values = c("#FA5858", "#64FE2E"), name = "Deposit") +
  theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.5))

# Subplot 3
fig <- fig + geom_violin(data = df, aes(x = education, y = balance, fill = deposit), width = 0.7) +
  labs(title = "Distribution of Balance by Education") +
  scale_fill_manual(values = c("#FA5858", "#64FE2E"), name = "Deposit")

# Show the plot
print(fig)

```
```{r}

# Create a new variable combining 'marital' and 'education'
df$marital_education <- paste(df$marital, df$education, sep = "/")

# Group by 'marital/education' and calculate the median balance
education_groups <- df %>%
  group_by(marital_education) %>%
  summarise(median_balance = median(balance)) %>%
  arrange(desc(median_balance))

# Define a color palette
colors <- scales::brewer_pal(palette = "Set3")(length(unique(education_groups$marital_education)))

# Create the bar plot with different colors
bar_plot <- ggplot(education_groups, aes(x = median_balance, y = marital_education, fill = marital_education)) +
  geom_bar(stat = "identity", alpha = 0.7) +
  scale_fill_manual(values = colors) +  # Use the defined color palette
  labs(title = "Median Balance by Educational/Marital Group", 
       x = "Median Balance", 
       y = "Educational/Marital Group") +
  theme_minimal()

# Display the plot
print(bar_plot)

```
```{r}
# Group by job and calculate the response rate
occupation_response <- df %>%
  group_by(job) %>%
  summarise(response_rate = mean(deposit == "yes"))

# Find the occupation with the highest response rate
targeted_occupation <- occupation_response %>%
  filter(response_rate == max(response_rate)) %>%
  pull(job)

cat("Targeted Occupation:", targeted_occupation, "\n")
```
```{r}
# Group by job and calculate the number of deposits
occupation_deposits <- df %>%
  filter(deposit == "yes") %>%
  group_by(job) %>%
  summarise(total_deposits = n())

# Find the occupation with the highest number of deposits
targeted_occupation <- occupation_deposits %>%
  filter(total_deposits == max(total_deposits)) %>%
  pull(job)

cat("Targeted Occupation (by deposits):", targeted_occupation, "\n")
```





```{r}
# Boxplot
ggplot(df, aes(x = job, y = age)) +
  geom_boxplot(fill = "#64FE2E") +
  labs(title = "Distribution of Ages by Occupation", x = "Occupation", y = "Age") +
  theme_minimal()

# Violin plot
ggplot(df, aes(x = job, y = age, fill = job)) +
  geom_violin() +
  labs(title = "Distribution of Ages by Occupation", x = "Occupation", y = "Age") +
  scale_fill_manual(values = c("#64FE2E", "#FA5858", "#FFD700", "#4169E1", "#FF69B4", "#8B4513", "#800080", "#00FFFF", "#FF4500", "#808080", "#FF8C00", "#8A2BE2")) +
  theme_minimal()
```



```{r}
ggplot(df, aes(x = balance, y = duration, color = deposit)) +
  geom_point() +
  labs(title = "Scatter Plot of Balance vs. Duration", x = "Balance", y = "Duration", color = "Deposit") +
  scale_color_manual(values = c("#FA5858", "#64FE2E")) +
  theme_minimal()
```



```{r}
# Order job variable
df$job <- factor(df$job, levels = c('unknown', 'blue-collar', 'entrepreneur', 'housemaid', 'management', 'retired', 'self-employed', 'services', 'student', 'technician', 'unemployed', 'admin.'))
df$job <- as.numeric(df$job) - 1  # Subtract 1 to make it 0-indexed

# Order marital variable
df$marital <- factor(df$marital, levels = c('unknown', 'divorced', 'married', 'single'))
df$marital <- as.numeric(df$marital) - 1  # Subtract 1 to make it 0-indexed

# Order default variable
df$default <- factor(df$default, levels = c('unknown', 'no', 'yes'))
df$default <- as.numeric(df$default == 'yes')  # Convert 'yes' to 1, others to 0

# Order housing variable
df$housing <- factor(df$housing, levels = c('unknown', 'no', 'yes'))
df$housing <- as.numeric(df$housing)  # Already binary, so no need to subtract 1

# Order loan variable
df$loan <- factor(df$loan, levels = c('unknown', 'no', 'yes'))
df$loan <- as.numeric(df$loan)  # Already binary, so no need to subtract 1

# Order education variable
df$education <- factor(df$education, levels = c('unknown', 'primary', 'secondary', 'tertiary'))
df$education <- as.numeric(df$education) - 1  # Convert to 0 for 'unknown', 1 for 'primary', 2 for 'secondary', 3 for 'tertiary'


# Order contact variable
df$contact <- factor(df$contact, levels = c('telephone', 'cellular'))
df$contact <- as.numeric(df$contact)  # Already binary, so no need to subtract 1

# Order month variable
df$month <- factor(df$month, levels = c('jan', 'feb', 'mar', 'apr', 'may', 'jun', 'jul', 'aug', 'sep', 'oct', 'nov', 'dec'))
df$month <- as.numeric(df$month)  # Subtract 1 to make it 0-indexed


# Convert deposit to binary
df$deposit <- as.numeric(df$deposit == 'yes')


# Display the first few rows of the updated dataset
head(df)

```


```{r}
# Drop 'contact' and 'poutcome' columns
df <- df[, !(names(df) %in% c("contact", "poutcome"))]
```




```{r}
cor_matrix <- cor(df[, c("age", "balance", "duration", "campaign", "pdays", "previous")])

# Print the correlation matrix
print(cor_matrix)

```
```{r}
library(corrplot)

# Set up the plotting area
par(mar = c(2, 2, 2, 2))  # Adjust the margins if needed

# Create a heatmap of the correlation matrix with correlation coefficients
corrplot(cor_matrix, method = "color", type = "full", order = "hclust", tl.cex = 0.8, addCoef.col = "black")

# Add a title
title(main = "Correlation Heatmap")

```

```{r}

# Bar plot of campaign distribution
barplot(table(df$campaign), main = "Distribution of Campaigns", xlab = "Campaign", ylab = "Count")
```




```{r}
summary(df)
colSums(is.na(df))

```

```{r}
# Create a binary treatment variable
df$treatment_binary <- ifelse(df$campaign %in% 1:4, 1, 0)

# Check the distribution of the new binary treatment variable
table(df$treatment_binary)
```



```{r}
# Load the necessary libraries
library(MatchIt)
library(WeightIt)
library(tidyverse)

# Specify the treatment and covariates
treatment_variable <- "treatment_binary"
covariates <- c("age", "job", "marital", "education", "default", "balance", "housing", 
                "loan", "day", "month", "duration", "pdays", "previous")

# Create a formula for the treatment variable
treatment_formula <- as.formula(paste(treatment_variable, "~", paste(covariates, collapse = "+")))

# Estimate the propensity scores
ps_model <- ps(treatment_formula, data = df, method = "binomial", maxit = 100)

# Estimate the ATE using the MatchIt package
matched_data <- matchit(treatment_formula, data = df, method = "nearest", ratio = 1)

# Calculate the ATE
ate_model <- lm(deposit ~ treatment_binary, data = match.data(matched_data))
ate <- mean(ate_model$coef[2])

# Display the ATE
cat("Estimated Average Treatment Effect (ATE):", round(ate, 4), "\n")

# Display more information about the regression model
summary(ps_model)
summary(ate_model)


```



```{r}
library(ggplot2)

# df is my data frame
df$campaign_binary <- ifelse(df$campaign <= 4, 1, 0)

# Plot the distribution of the outcome variable for treated and control groups
ggplot(df, aes(x = deposit, fill = factor(campaign_binary))) +
  geom_bar(position = "dodge") +
  labs(title = "Distribution of Deposit by Treatment Group",
       x = "Deposit",
       y = "Count",
       fill = "Campaign Group") +
  theme_minimal()

```
```{r}
summarise(matched_data)

```

```{r}
# Assuming 'matched_data' has been previously calculated
library(tidyverse)

# Calculate standardized mean differences before and after matching
balance_table <- map_dfr(covariates, function(covariate) {
  before_match <- df %>%
    group_by(treatment_binary) %>%
    summarize(mean_treat = mean(.data[[covariate]], na.rm = TRUE))

  after_match <- matched_data %>%
    group_by(treatment_binary) %>%
    summarize(mean_treat = mean(.data[[covariate]], na.rm = TRUE))

  data.frame(
    variable = covariate,
    standardized.diff = (after_match$mean_treat[2] - after_match$mean_treat[1]) /
      sqrt((before_match$mean_treat[1] + before_match$mean_treat[2]) / 2)
  )
})

# Plot standardized mean differences
balance_plot <- ggplot(balance_table, aes(x = as.factor(variable), y = standardized.diff)) +
  geom_bar(stat = "identity", fill = "skyblue") +
  ggtitle("Standardized Mean Differences Before and After Matching") +
  xlab("Covariate") +
  ylab("Standardized Mean Difference") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

# Display the balance plot
print(balance_plot)


```





```{r}
# and 'deposit' is the outcome variable
boxplot(deposit ~ treatment_binary, data = df, col = c("blue", "red"),
        main = "Average Treatment Effect (ATE) Visualization",
        xlab = "Treatment Group", ylab = "Outcome Variable")

```

```{r}
# Histogram
hist(df$deposit[df$treatment_binary == 0], col = "blue", xlim = c(min(df$deposit), max(df$deposit)),
     main = "Distribution of Outcome Variable by Group",
     xlab = "Outcome Variable", ylab = "Frequency", density = 30, alpha = 0.5)
hist(df$deposit[df$treatment_binary == 1], col = "red", add = TRUE, density = 30, alpha = 0.5)
legend("topright", legend = c("Control", "Treatment"), fill = c("blue", "red"))

# Density plot
plot(density(df$deposit[df$treatment_binary == 0]), col = "blue", lwd = 2,
     main = "Kernel Density Plot of Outcome Variable by Treatment Status",
     xlab = "Outcome Variable", ylab = "Density")
lines(density(df$deposit[df$treatment_binary == 1]), col = "red", lty = 2, lwd = 2)
legend("topright", legend = c("Control", "Treatment"), fill = c("blue", "red"))
```
```{r}

```


